\section*{Erkl\"arung zur Abschlussarbeit gem\"a\ss\ \S\ 22 Abs.\ 7 und \S\ 23 Abs.\ 7 APB TU Darmstadt}

Hiermit versichere ich, Matthias Heinz, die vorliegende Master-Thesis gem\"a\ss{} \S\ 22 Abs.\ 7 APB der TU Darmstadt ohne Hilfe Dritter und nur mit den angegebenen Quellen und Hilfsmitteln angefertigt zu haben. Alle Stellen, die Quellen entnommen wurden, sind als solche kenntlich gemacht worden. Diese Arbeit hat in gleicher oder \"ahnlicher Form noch keiner Pr\"ufungsbeh\"orde vorgelegen.

Mir ist bekannt, dass im Falle eines Plagiats (\S\ 38 Abs. 2 APB) ein T\"auschungsversuch vorliegt, der dazu f\"uhrt, dass die Arbeit mit 5,0 bewertet und damit ein Pr\"ufungsversuch verbraucht wird. Abschlussarbeiten d\"urfen nur einmal wiederholt werden.

Bei der abgegebenen Thesis stimmen die schriftliche und die zur Archivierung eingereichte elektronische Fassung gem\"a\ss{} \S\ 23 Abs. 7 APB \"uberein.

\vskip3ex \hrule \vskip3ex

English translation for information purposes only:

\textbf{Thesis statement pursuant to \S\ 22 paragraph 7 and \S\ 23 paragraph 7 of APB TU Darmstadt}

I herewith formally declare that I, Matthias Heinz, have written the submitted Master's thesis independently pursuant to \S\ 22 paragraph 7 of APB TU Darmstadt. I did not use any outside support except for the quoted literature and other sources mentioned in the paper. I clearly marked and separately listed all of the literature and all of the other sources which I employed when producing this academic work, either literally or in content. This thesis has not been handed in or published before in the same or similar form.

I am aware, that in case of an attempt at deception based on plagiarism (\S\ 38 paragraph 2 APB), the thesis would be graded with 5,0 and counted as one failed examination attempt. The thesis may only be repeated once.

In the submitted thesis the written copies and the electronic version for archiving are pursuant to \S\ 23 paragraph 7 of APB identical in content.

\vskip3ex \hrule

\vskip5ex
Darmstadt, den 13.~Oktober 2020
\vskip6ex
\rule{0.5\textwidth}{0.4pt}

{\normalsize(Matthias Heinz)}
